flowers-pilot-analysis

### 2021-07-22 code/aa-flowers-pilot_analysis.Rmd
moved preprocessing to script and joined data files

```{r set-up, include=F}
#knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
#knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
#options(knitr.table.format = "html")
library(tidyverse)
library(jsonlite)
library(here)

theme_set(theme_bw())

data_target = "collabmulti_pilot0"
##Data import constants
data_location=paste0("data/",data_target)
date_start=lubridate::ymd('2021-07-19')
image_location=paste0(here("figs",data_target))

#library(rlang)
#library(lme4)
#library(brms)
#library(rstan)
#rstan_options(auto_write = TRUE)
#options(mc.cores = parallel::detectCores())
#model_location="code/models"

@@

```{r}
# This was for determining participant bonuses using the version of data with PID
# d.treatments <- read_csv(here(data_location, 'treatments.csv')) %>% rename(treatmentId=`_id`)
# 
# d.games <- read_csv(here(data_location, 'games.csv')) %>%
#   select(gameId=`_id`, treatmentId, playerIds) %>%
#   left_join(d.treatments) %>%
#   mutate(playerIds=str_split(playerIds,",")) %>%
#   unnest(playerIds) %>%
#   select(playerId=playerIds, name)
# 
# d.players <- read_csv(here(data_location, 'players.csv')) %>%
#   rename(playerId=`_id`) %>%
#   left_join(d.games) %>%
#   select(data.bonus, playerId,id,data.bonus,name) %>%
#     filter(!is.na(name)) %>%
#   mutate(pc_bonus=case_when(
#     name=="fourRotate" ~ 3,
#     name=="threeRotate" ~ 1.5,
#     T ~ 0
#   )) %>%
#   mutate(bonus=round(data.bonus+pc_bonus,2),
#          cost=round(bonus*4/3,2)) %>% write_csv(here(data_location, "player_payments.csv")) %>% select(id,bonus) %>% write_csv(here(data_location,"for_prolific.csv"))
```

# Pre-process

We need:
1) game info with treatment parameters
2) context for each round (what were participant's options? max utility based on game conditions?)
3) round results (what did participants select each round?)
4) chat (what did individual participants say each round)
5) feedback/demographics

```{r helper-functions}
ParseJSONColumn <- function(x) {
  str_c("[ ", str_c(x, collapse = ",", sep=" "), " ]")  %>% 
    fromJSON(flatten = T)
}

extract_context_info <- function(context_key){
  return(str_extract(context_key, "[^.]*$"))
}
```

Get info about the games and treatments
- We need each game, the 
```{r game-preprocessing}
d.games.raw <- read_csv(here(data_location, 'games.csv')) %>% 
  rename(gameId = `_id`) %>% 
  filter(createdAt >= date_start) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE))

d.treatments.raw <- read_csv(here(data_location, 'treatments.csv')) %>% 
  rename(treatmentId = `_id`) %>%
  #filter(createdAt >= date_start) %>%
  mutate(factorIds = str_split(factorIds, pattern=",")) %>%
  unnest(factorIds) %>% rename(factorId = factorIds)

d.factors.raw <- read_csv(here(data_location, 'factors.csv'))%>% 
  rename(factorId = `_id`)

d.factor_types.raw <- read_csv(here(data_location, 'factor-types.csv')) %>%
  rename(factorTypeId = "_id",
         factorName = "name")

d.factors <- d.factors.raw %>% 
  left_join(d.factor_types.raw %>% 
              select(factorTypeId, factorName))

d.treatments <- d.treatments.raw %>% 
  left_join(d.factors %>% 
              select(factorId, factorName, value)) %>%
  pivot_wider(id_cols = c(treatmentId, name, createdAt), 
              names_from = factorName, values_from = value)

d.players <- read_csv(here(data_location, 'players.csv')) %>%
  rename(playerId = `_id`) %>% 
  filter(createdAt >= date_start) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE))

d.games <- d.games.raw %>% left_join(d.treatments %>% 
                                       select(-createdAt)) %>%
  janitor::remove_empty() %>%
  #select out the nonuseful columns
  select(-c(gameLobbyId, treatmentId, batchId, targetSet, justStarted, submitCode, roundIds)) %>%
  separate(col = playerIds, sep = ",", into = c("player_1", "player_2", "player_3")) %>% 
  pivot_longer(cols = starts_with("player_"), names_to = "playerNum", values_to = "playerId") %>%
  left_join(d.players %>% select(playerId, readyAt)) %>%
  mutate(game_length = finishedAt - readyAt) %>%
  group_by(across(gameId:chatEnabled)) %>%
  summarize(gameLength = max(game_length)) %>% ungroup()
```

Round info
For each round, we want to know the context...
- which flowers were available
- the utility of each flower

We also want to have a report for each round including...
- which participants selected which flowers
- the time the participants took to select
- the utility of the flower the participants selected

```{r}
d.round_results.raw <- read_csv(here(data_location,'rounds.csv'), guess_max=10000) %>% 
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T))

#try pivot_longer instead of gather??
d.round_results <- d.round_results.raw  %>% 
  #filter out rounds where no one made a selection
  filter(!is.na(chat)) %>%
  select(-chat, -context) %>%
  mutate_at(vars(starts_with('player')), as.character) %>%
  pivot_longer(cols = starts_with('player'), 
               names_to = c('blah', 'playerId', 'info'), 
               values_to = "value",
               names_sep = "_",
               values_drop_na = TRUE) %>%
  pivot_wider(names_from = "info", values_from = "value") %>%
  select(-blah) %>%
  mutate_at(c("time", "utility"), as.numeric) %>%
  mutate(utility = ifelse(response == "false", 0, utility)) %>%
  #TODO: some times are negative?? interesting
  mutate(time = abs(as.numeric(time)/1000)) %>%
  rename(time_sec = time, playerResponse = response, playerUtility = utility) %>%
  arrange(createdAt, gameId, blockNum, repNum)

#exclude blocks with <12 completed rounds
rounds_exclude <- d.round_results %>% group_by(gameId, blockNum) %>% tally() %>% filter(n!=36) %>% select(gameId,blockNum)
d.round_results.final <-  d.round_results %>% anti_join(rounds_exclude)
```
```{r}
game_completion <- d.round_results %>% 
  group_by(gameId) %>% 
  summarize(num_rounds=max(trialNum+1)) %>% 
  left_join(d.games%>% ungroup() %>% select(gameId, condition, chat=chatEnabled, gameLength)) %>%
  mutate(gameComplete = ifelse(num_rounds == 48, TRUE, FALSE))
#knitr::kable(summary)
message("Full games")
game_completion %>% filter(num_rounds==48)
message("Partial games")
game_completion %>% filter(num_rounds!=48) 
```

>>>>

```{r set-up, include=F}
library(tidyverse)
library(jsonlite)
library(here)
source(here("code/preprocessing/00_preprocessing_functions.R"))
theme_set(theme_bw())

##Data import constants
date_start=lubridate::ymd('2021-07-19')
image_location=here("figs")

@@

# Pre-process
```{r process-data, message=FALSE, warning=FALSE}
data_list <- c("technical_pilots", "collabmulti_pilot0", 
               "collabmulti_20", "compet_20")
process_all_data(data_list)
join_all_data()
```

```{r read-processed-date, message=FALSE}
d.players <- read_csv(here("data/processed_data/joined_data/players.csv")) %>% distinct()
d.games <- read_csv(here("data/processed_data/joined_data/games.csv")) %>% distinct()
d.rounds <- read_csv(here("data/processed_data/joined_data/rounds.csv")) %>% distinct()
d.raw_chat <- read_csv(here("data/processed_data/joined_data/raw_chat.csv")) %>% distinct()
```

```{r}
#exclude BLOCKS with <12 completed (all 3 participants responded) rounds
rounds_exclude <- d.rounds %>% group_by(gameId, blockNum) %>% tally() %>% filter(n!=36) %>% select(gameId,blockNum)

d.rounds.final <-  d.rounds %>% anti_join(rounds_exclude)
d.raw_chat.final <- d.raw_chat %>% anti_join(rounds_exclude) %>% write_csv(here("data/processed_data/joined_data/filtered_raw_chat.csv"))
```

```{r}
game_completion <- d.round_results %>% 
  group_by(gameId) %>% 
  summarize(num_rounds=max(trialNum+1)) %>% 
  left_join(d.games%>% ungroup() %>% select(gameId, condition, chat=chatEnabled, gameLength)) %>%
  mutate(gameComplete = ifelse(num_rounds == 48, TRUE, FALSE))
#knitr::kable(summary)
message("Full games")
game_completion %>% filter(num_rounds==48)
message("Partial games")
game_completion %>% filter(num_rounds!=48) 
```
